---
title: "Time Series Analysis"
author: "MessaA"
date: "July 20, 2016"
output:
  html_document:
    toc: yes
  pdf_document:
    number_sections: yes
    toc: yes
---  

## Q1. hsales data  

### a. Download and plot hsales data. Can you identify seosonal flactuation or trend?
```{r}
library(fpp) #fpp package needed to be installed
data(hsales)
plot(hsales)
```  

#### It looks like there are both seasonal and trend fluctuations

### b. Use classical decomposition to calculate the trend-cycle and seosonal indices.Do the results support the graphical interpretation from part(a)?  
```{r}
fithsd <- decompose(hsales)
plot(fithsd)
```  

#### Yes they do, the decomposition clearly shows all that fluctuations (seasonal and trend)

### c. compute and plot the seasonally adjusted data.
```{r}
hsadj <- seasadj(fithsd)
plot(hsadj)
```  

### d. change one observation to be an outlier  (say 500) and recompute the the seasonally adjusted data. What is the effect of the outlier?  
```{r}
hsales2 <- ts(c(hsales[1:137],hsales[138]+500,hsales[139:275]),start=c(1973,1),frequency=12)
plot(hsales2)
```  

#### The outlier causes the house sales to have a sharp change at the middle where the outlier is added at. 

### e. does it make any diffrence if the outlier is near end rather than in the middle of the time series?  
```{r}
hsales3 <- ts(c(hsales[1:269],hsales[270]+500,hsales[271:275]),start=c(1973,1),frequency=12)
plot(hsales3)
```  

#### Yes it does. As the outlier moves towards the end the change (sharp peak) moves with it too

### f. Now use STL to decompose the series  
```{r}
fit <- stl(hsales, s.window=5)
plot(fit)
```  

## Q2. Volatility Analysis  

### a. download the data  
```{r}
library(tseries)

ADPdata <- get.hist.quote('ADP',quote="Close")
length(ADPdata)
```  
### b. calculate log returns  
```{r}
ADPret <- log(lag(ADPdata)) - log(ADPdata)
length(ADPret)
```  
### c. calculate volatility measure   
```{r}
ADPvol <- sd(ADPret) * sqrt(250) * 100
ADPvol
```  
### d. calculate volatility measure with continous lookback window  
```{r}
get
Vol <- function(d, logrets)
{
var = 0
lam = 0
varlist <- c()
for (r in logrets) {
lam = lam*(1 - 1/d) + 1
	var = (1 - 1/lam)*var + (1/lam)*r^2
	varlist <- c(varlist, var)
	}
sqrt(varlist)
}
volest1 <- Vol(10,ADPret)
volest2 <- Vol(30,ADPret)
volest3 <- Vol(100,ADPret)
```  

### e. plot the results with a volatility curve overlay  
```{r}
plot(volest1,type="l")
lines(volest2,type="l",col="yellow")
lines(volest3, type = "l", col="purple")
```  

#### The volatility plot shows there is a high risk for the ADP return of weight =10 at arround the beginning, between 1000 and 2000, and between 2000 and 3000 indices. Those risks are getting better and better as the weight increases to 100. 
